SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-04 docs/questioning.tex
more work

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

\begin{figure*} [ht]
\begin{center}
\leavevmode
\includegraphics[scale=0.65]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of web application
attack countermeasures ({\sc draft}).}
\end{figure*}

@@

Policy enforcement mechanisms that detect {\sc csrf}
attacks are usually implemented in the form of a
server-side proxy (locus {\sc y})
interposing on the client-server communication, and modifying
it. {\it NoForge}~\cite{JKK06a}
parses the {\sc html} server responses
and adds a token to every {\sc url} referring to this
server. Then it associates the token with the cookie
representing the session {\sc id} for the application.
When a request is received, the mechanism checks
if the request contains the token related
to the session {\sc id}. A disadvantage of NoForge
is that {\sc html} that is dynamically created within
the browser will not include the token.
Thus, sites that create their {\sc html} on the client
will remain vulnerable. In addition, it does not
support cross-origin requests.
{\it j{\sc csrf}}~\cite{PS11}
has a very similar functionality and meanwhile
addresses the above problems.
Finally, {\it CsFire}~\cite{DDHPJ10}
examines cross-domain interactions,
to design a cross-domain policy.
The policy is based on the concept of a relaxed
same-origin policy that allows communication between
sub-domains of the same registered domain.

@@

There are different implementations of these approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}).
However, this is a simplistic approach that may
lead to many false positives.
The following schemes apply further checks when
they identify that tainted data have reached a sink.
In particular, {\it Xu et al.}~\cite{XBS06}
tracks taint information at the level of bytes in memory.
To distinguish between legitimate and malicious uses
of untrusted data that reach a sink,
they search the data for suspicious symbols by using
regular expressions. {\sc csse}~\cite{PB05} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and other. When tainted data reaches a sink {\sc csse} performs
syntactic checks it based on the aforementioned metadata
(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
in a similar way. To obtain metadata, it takes advantage
of specific features provided by {\sc php}.
Note that the above schemes detect potential attacks
in locus {\sc z}. This automatically means that they
cannot detect non-persistent JavaScript-driven
{\sc xss} attacks. Although they can be
modified to do so. {\sc wasc}~\cite{NLC07} 
though, can deal with such attacks because it
analyzes {\sc html} responses to check
if there are tainted data that contain scripts (locus {\sc y}).
A recent study showed that there are ways to circumvent
the majority of the above schemes~\cite{NBR14}.
Furthermore, most of them are hard to deploy since
the majority of input vectors, string operations
and output vectors must be instrumented.

>>>>

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references:
locus {\sc x}~\cite{KKVJ06,KJKV09,TNH07,NSS06,APKLM10,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,APKLM10,VFJKKV07,SLMS14},
locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,MKS09,HO05,HO06,HO05b,SMS13},
locus $\Omega$~\cite{BK04,LLW02}.}
\end{figure*}

@@

\begin{figure*} [ht]
\begin{center}
\leavevmode
\includegraphics[scale=0.65]{defenses.pdf}
\end{center}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application
attacks, based on executable source code injectiion. For each approach
we provide the references that present corresponding mechanisms:
{\bf 1}~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,LV09},
{\bf 2}~\cite{BK04,JB07,GC09,APKLM10},
{\bf 3}~\cite{BWS05,SW06},
{\bf 4}~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\bf 5}~\cite{LLW02,HO05,HO06,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
{\bf 6}~\cite{BV08,LV09,SMS13}.}
\end{figure*}

@@

Policy enforcement mechanisms that detect {\sc csrf}
attacks are usually implemented in the form of a
server-side proxy (locus {\sc y})
interposing on the client-server communication, and modifying
it. {\it NoForge}~\cite{JKK06a}
parses the {\sc html} server responses
and adds a token to every {\sc url} referring to this
server. Then it associates the token with the cookie
representing the session {\sc id} for the application.
When a request is received, the mechanism checks
if the request contains the token related
to the session {\sc id}. A disadvantage of NoForge
is that {\sc html} that is dynamically created within
the browser will not include the token.
Thus, sites that create their {\sc html} on the client
will remain vulnerable. In addition, it does not
support cross-origin requests.
{\it j{\sc csrf}}~\cite{PS11}
has a very similar functionality and meanwhile
addresses the above problems.
Finally, {\it CsFire}~\cite{DDHPJ10}
examines cross-domain interactions, to design a
cross-domain policy on the client's side (locus {\sc x}).
The policy is based on the concept of a relaxed
same-origin policy that allows communication between
sub-domains of the same registered domain.

@@

There are different implementations of these approach
in terms of how the tainted data is marked and observed,
and how attacks are detected.
For example, {\it Haldar et al.}~\cite{HCF05} have implemented
their scheme for the Java Virtual Machine ({\sc jvm})
where they instrument various classes. When a
tainted string is used as an argument to a sink method
then an exception is raised (locus {\sc z}).
However, this is a simplistic approach that may
lead to many false positives.
The following schemes apply further checks when
they identify that tainted data have reached a sink
(locus {\sc z}).
In particular, {\it Xu et al.}~\cite{XBS06}
tracks taint information at the level of bytes in memory.
To distinguish between legitimate and malicious uses
of untrusted data that reach a sink,
they search the data for suspicious symbols by using
regular expressions. {\sc csse}~\cite{PB05} associates
tainted data with specific metadata. Such metadata include
the origins of tainted data, its propagation within the application
and other. When tainted data reaches a sink {\sc csse} performs
syntactic checks it based on the aforementioned metadata
(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
in a similar way. To obtain metadata, it takes advantage
of specific features provided by {\sc php}.
% Note that the above schemes detect potential attacks
% in locus {\sc z}. This automatically means that they
% cannot detect non-persistent JavaScript-driven
% {\sc xss} attacks. Although they can be
% modified to do so.
{\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
if there are tainted data that contain scripts (locus {\sc y}).
A recent study showed that there are ways to circumvent
the majority of the above schemes~\cite{NBR14}.
Furthermore, most of them are hard to deploy since
the majority of input vectors, string operations
and output vectors must be instrumented.
